### 2020-12-04 doc/manuscript/Dow_manuscript.Rmd
switch to regular word formatting
ugly, but solves section/ figure numbering issues

---
title: ''
output:
  bookdown::word_document2: 
    reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
    fig_caption: yes
bibliography: references.bib
csl: global-change-biology.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: ''
output:
  word_document
  #bookdown::word_document2: 
    #reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
    #fig_caption: yes
bibliography: references.bib
csl: global-change-biology.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
